A Cross-Benchmark Comparison of Learning to Rank Methods

### 2014-05-19 cikm_paper/paper.tex
conclusion + repeat caption

\section{Conclusions}
We will now look back on our first research question using the knowledge gained with the cross-benchmark comparison.
\begin{description}
\item[RQ1] What are the best performing learning to rank algorithms in terms of accuracy on relevant benchmark datasets?\\
\end{description}
Although no closing arguments can be formulated on which learning to rank methods are most accurate, a lot of insight has been gained with the cross-benchmark comparison on which methods tend to perform better than others.\\

@@

Method & NWN & \#ds && NWN & \#ds && NWN & \#ds && NWN & \#ds && WM & IWN & NWN \\ \midrule

>>>>

\section{Conclusions}
Although no closing arguments can be formulated on which learning to rank methods are most accurate, a lot of insight has been gained with the cross-benchmark comparison on which methods tend to perform better than others.\\

@@

Method & NWN & \#ds && NWN & \#ds && NWN & \#ds && NWN & \#ds && WM & IWN & NWN \\ \midrule\endhead
